
\chapter{Results} \label{c:results}
\todo{Tutto da scrivere:
\begin{description}
\item[Domanda stabile subcritica]
\item[Domanda stabile supercritica]
\item[Riduzione di capacità alla fine del corridoio] per vedere se tiene le code a monte o fa andare tutti a morire in fondo.
\end{description}}

\section{Algorithm Parameters}
This section presents results of the preliminary studies aimed at determining an optimal choice of parameters for the Genetic Algorithm.
\todo{Genetic Algorithm parameters, population priming, dynamic weighting effects}

\subsection{Population Size}

\subsection{Population Priming} \label{s:poppriming}

Slack Bandwidth section \ref{s:slackband} show it is much better than reg band for similar "progression" objectives (travel times) for a two-way band max problem with weights proportional to flows. \todo{rant about how novel this is.}

Show effect of initial population mix on convergence.

\section{Test Networks}

\subsubsection*{Eight Junction corridor with side flows} \label{s:sync8}
\todo{Describe the features of sync8 and why it is representative of the problem.}



\section{Overall Cost Function Improvement}
\todo{Demonstrate capability to improve over the SlackBand solution.}

\section{Comparison with Balance}
Run hour long rolling optimisation and present in detail the evolution of traffic conditions.\todo{Maybe not bc balance won't cooperate.}


\section{Performance in Micro Simulation}
\todo{Confirm effectiveness of solutions in a microsimulator, since in TRE they obviously work.}

\section{Performance}

\subsection{Look-Ahead Window Size} \label{res:windowsizing}

\todo{Considerations upon computation time issues and applicability, scaling.}
Different corridor lengths.

\todo{can be used for planning!}

\section{Conclusions and Future Work}

